---
title: "Project Proposal"
subtitle: "due October 11, 2021 by 11:59 PM "
author: "G.I. Joe - Isabella Rundell and Grace Vo"
date: "October 11, 2021"
output: pdf_document
---

# Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)
``` 

# Load Data
```{r load-data, message = F}
glimpse(Drug_Consumption, width = getOption("width"))
```

# Introduction and Data, including Research Questions

(The introduction should introduce your general research question and your data (where it came from, how it was collected, what are the cases, what are the variables, etc.). Your research questions should be clearly specified. The motivation for your research question should be clear, with citations to relevant literature as appropriate.)

# Glimpse

(Please use `glimpse` for your data, uploaded into the data folder, here.)

# Data Analysis Plan

(Specify the outcome (response, Y) and predictor (explanatory, X) variables you will use to answer your question, as well as the comparison groups you will use, if applicable. You may include very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. Note the statistical method(s) that you believe will be useful in answering your question(s). 
What results from these specific statistical methods are needed to support your hypothesized answer?)

Y: drug use
X: personality scores
comparison groups: gender and age cats

Ideas for visualization:
-bar plot with age on x-axis, dodged by gender, faceted by drug type

To modify data:
-group drug usage ratings (never used, used a long time ago, used in past month)

Stat methods:
-bootstrapped null distribution?
-t-test: is there sufficient evidence that lower personality scores lead to higher levels of drug use?
