---
title: "Exploring personality scores and drug use: factors that contribute to increased use of psilocybin (magic mushrooms)"
author: 'G.I. Joe: Isa Rundell and Grace Vo'
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: solarized-light
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE, echo = FALSE}
# Add any additional packages you need to this chunk
# Remove any packages from this list that you're not using
install.packages("taRifx")
library(tidymodels)
library(xaringanthemer)
library(tidyverse)
library(knitr)
library(dplyr)
library(taRifx)
library(infer)
library(parsnip)
library(tidyr)
library(reshape2)
library(ragg)
library(palmerpenguins)
library(patchwork)
library(base)
```

```{r setup, include=FALSE, echo = FALSE}
# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r setup1, include=FALSE, echo = FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load-data, include=FALSE, echo = FALSE}
drug <- readr::read_csv("Drug_Consumption.csv")
```

```{r style-slides, echo = FALSE}
style_xaringan(
  title_slide_background_image = "img/purplemaroon.png"
)
```


## Introducing the Data

```{r penguins-table, echo = FALSE}
kable(head(drug), format = "html")
```

---

## Research Questions

--

- For which personalities is there a significant correlation with mushroom use, positive or negative?

--

- For which demographic observations, not including ethnicity, is there a significant correlation to mushroom use?

---
## Correlation Matrix

```{r heatmap, echo = FALSE}
drug1 <- drug %>%
  mutate(across(Alcohol:VSA,destring))

drug1[,14:32] <- sapply(drug1[,14:32],as.numeric)
drugmeans <- colMeans(drug1[ , 14:32])

numdrug <- drug1 %>%
  mutate(Age = replace(Age, Age == "18-24", 0), Age = replace(Age, Age == "25-34", 1), Age = replace(Age, Age == "35-44", 2), Age = replace(Age, Age == "45-54", 3), Age = replace(Age, Age == "55-64", 4), Age = replace(Age, Age == "65+", 5), Gender = replace(Gender, Gender == "F", 0), Gender = replace(Gender, Gender == "M", 1), Education = replace(Education, Education == "Left school before 16 years", 0), Education = replace(Education, Education == "Left school at 16 years", 1), Education = replace(Education, Education == "Left school at 17 years", 2), Education = replace(Education, Education == "Left school at 18 years", 3), Education = replace(Education, Education == "Some college or university, no certificate or degree", 4), Education = replace(Education, Education == "Professional certificate/ diploma", 5), Education = replace(Education, Education == "University degree", 6), Education = replace(Education, Education == "Masters degree", 7), Education = replace(Education, Education == "Doctorate degree", 8), Country = replace(Country, Country == "Australia", 0), Country = replace(Country, Country == "Canada", 1), Country = replace(Country, Country == "New Zealand", 2), Country = replace(Country, Country == "Other", 3), Country = replace(Country, Country == "Republic of Ireland", 4), Country = replace(Country, Country == "UK", 5), Country = replace(Country, Country == "USA", 6), Ethnicity = replace(Ethnicity, Ethnicity == "Asian", 0), Ethnicity = replace(Ethnicity, Ethnicity == "Black", 1), Ethnicity = replace(Ethnicity, Ethnicity == "Mixed-Black/Asian", 2), Ethnicity = replace(Ethnicity, Ethnicity == "Mixed-White/Asian", 3), Ethnicity = replace(Ethnicity, Ethnicity == "Mixed-White/Black", 4), Ethnicity = replace(Ethnicity, Ethnicity == "Other", 5), Ethnicity = replace(Ethnicity, Ethnicity == "White", 6))
numdrug <- mutate_all(numdrug, function(x) as.numeric(as.character(x)))
numdrug2 = select(numdrug, -Alcohol, -Amphet, -Amyl, -Benzos, -Caff, -Cannabis, -Choc, -Coke, -Crack, -Ecstasy, -Heroin, -Ketamine, -Legalh, -LSD, -Meth, -Nicotine, -VSA, -Semer)
#head(numdrug2)
correlation_matrix <- round(cor(numdrug2),2)
#head(correlation_matrix)
  get_upper_tri<-function(correlation_matrix){
    correlation_matrix[lower.tri(correlation_matrix)] <- NA
    return(correlation_matrix)
  }
  upper_tri <- get_upper_tri(correlation_matrix)
library(reshape2)
melted_cormat <- melt(upper_tri, na.rm = TRUE)
library(ggplot2)
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "#8a02b2", high = "#560219", mid = "#FAF9F6", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation (Pearson)") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 60, vjust = 1, 
    size = 10, hjust = 1), axis.text.y = element_text(vjust = 1, size = 10, hjust = 1))+
 coord_fixed() + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 1) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.75, 0.75),
  legend.direction = "horizontal",
  legend.key.size = unit(0.05, 'cm'))+
  guides(fill = guide_colorbar(barwidth = 9, barheight = 1,
                title.position = "top", title.hjust = 0.5))
```

---

## Mushroom User by Gender

```{r data-tidying, echo = FALSE}
drug_clean <- numdrug %>%
  mutate(Alcohol_User = as.factor(ifelse(Alcohol > 1, "yes", "no")), 
         Amphetamine_User = as.factor(ifelse(Amphet > 1, "yes", "no")), 
         AmylNitrite_User = as.factor(ifelse(Amyl > 1, "yes", "no")),
         Benzos_User = as.factor(ifelse(Benzos > 1, "yes", "no")),
         Caffeine_User = as.factor(ifelse(Caff > 1, "yes", "no")), 
         Cannabis_User = as.factor(ifelse(Cannabis > 1, "yes", "no")), 
         Chocolate_User = as.factor(ifelse(Choc > 1, "yes", "no")), 
         Cocaine_User = as.factor(ifelse(Coke > 1, "yes", "no")), 
         Crack_User = as.factor(ifelse(Crack > 1, "yes", "no")), 
         Ecstasy_User = as.factor(ifelse(Ecstasy > 1, "yes", "no")), 
         Heroine_User = as.factor(ifelse(Heroin > 1, "yes", "no")), 
         Ketamine_User = as.factor(ifelse(Ketamine > 1, "yes", "no")), 
         LegalHighs_User = as.factor(ifelse(Legalh > 1, "yes", "no")), 
         LSD_User = as.factor(ifelse(LSD > 1, "yes", "no")), 
         Meth_User = as.factor(ifelse(Meth > 1, "yes", "no")), 
         Mushrooms_User = as.factor(ifelse(Mushrooms > 1, "yes", "no")),
         Nicotine_User = as.factor(ifelse(Nicotine > 1, "yes", "no")),
         Semeron_User = as.factor(ifelse(Semer > 1, "yes", "no")), 
         VSA_User = as.factor(ifelse(VSA > 1, "yes", "no")))

drug_clean_2 <- drug1 %>%
    mutate(Alcohol_User = as.factor(ifelse(Alcohol > 1, "yes", "no")), 
         Amphetamine_User = as.factor(ifelse(Amphet > 1, "yes", "no")), 
         AmylNitrite_User = as.factor(ifelse(Amyl > 1, "yes", "no")),
         Benzos_User = as.factor(ifelse(Benzos > 1, "yes", "no")),
         Caffeine_User = as.factor(ifelse(Caff > 1, "yes", "no")), 
         Cannabis_User = as.factor(ifelse(Cannabis > 1, "yes", "no")), 
         Chocolate_User = as.factor(ifelse(Choc > 1, "yes", "no")), 
         Cocaine_User = as.factor(ifelse(Coke > 1, "yes", "no")), 
         Crack_User = as.factor(ifelse(Crack > 1, "yes", "no")), 
         Ecstasy_User = as.factor(ifelse(Ecstasy > 1, "yes", "no")), 
         Heroine_User = as.factor(ifelse(Heroin > 1, "yes", "no")), 
         Ketamine_User = as.factor(ifelse(Ketamine > 1, "yes", "no")), 
         LegalHighs_User = as.factor(ifelse(Legalh > 1, "yes", "no")), 
         LSD_User = as.factor(ifelse(LSD > 1, "yes", "no")), 
         Meth_User = as.factor(ifelse(Meth > 1, "yes", "no")), 
         Mushrooms_User = as.factor(ifelse(Mushrooms > 1, "yes", "no")),
         Nicotine_User = as.factor(ifelse(Nicotine > 1, "yes", "no")),
         Semeron_User = as.factor(ifelse(Semer > 1, "yes", "no")), 
         VSA_User = as.factor(ifelse(VSA > 1, "yes", "no")))
```


```{r mushrooms-vs-gender, echo = FALSE}
ggplot(drug_clean_2, aes(x = Gender,
             fill = Mushrooms_User)) +
  geom_bar() +
  labs(x="Gender",
       y = "Count",
       title="Figure 3: Mushroom User by Gender",
       fill = "Mushrooms User") + 
  scale_fill_manual(values=c("#8a02b2","#560219")) 
```

---

## Logistic Regression: Gender

```{r logistic-reg-gender, echo = FALSE}
drug_clean_2$Gender=relevel(factor(drug_clean_2$Gender), ref = "F")
fit_multi_gender <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(Mushrooms_User ~ Gender, data=drug_clean_2, family="binomial")
result1<-tidy(fit_multi_gender, conf.int=TRUE, exponentiate=TRUE)
print(result1)
```

---

## Mushroom User by Country


```{r, echo = FALSE}
ggplot(drug_clean_2, aes(x = Country,
             fill = Mushrooms_User)) +
  geom_bar(position = "fill") +
  labs(x="Country",
       y = "Proportion",
       title="Figure 5: Mushroom User by Country",
       fill = "Mushrooms User") + 
  scale_fill_manual(values=c("#8a02b2","#560219")) +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, 
    size = 10, hjust = 1), axis.text.y = element_text(vjust = 1, size = 10, hjust = 1))

```

---


## Logistic Regression: Country

```{r log-reg-country, echo = FALSE}
drug_clean_2$Country=relevel(factor(drug_clean_2$Country), ref = "USA")
fit_multi_country <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(Mushrooms_User ~ Country, data=drug_clean_2, family="binomial")
result4<-tidy(fit_multi_country, conf.int=TRUE, exponentiate=TRUE)
print(result4)
```

---

## Mushroom User by Education Level


```{r, echo = FALSE}
level_order <- factor(drug_clean_2$Education, level = c('Left school before 16 years', 'Left school at 16 years', 'Left school at 17 years', 'Left school at 18 years', 'Some college or university, no certificate or degree', 'University degree', 'Masters degree', 'Professional certificate/ diploma', 'Doctorate degree'))

ggplot(drug_clean_2, aes(x = level_order,
             fill = Mushrooms_User)) +
  geom_bar(position = "fill")  +
  labs(x="Education Level",
       y = "Proportion",
       title="Figure 7: Mushroom User by Education Level",
       fill = "Mushrooms User") + 
  scale_fill_manual(values=c("#8a02b2","#560219")) +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, 
    size = 6, hjust = 1), axis.text.y = element_text(vjust = 1, size = 8, hjust = 1))
```


---

## Logistic Regression: Education Level


```{r log-reg-edu, echo = FALSE}
drug_clean_2$Education=relevel(factor(drug_clean_2$Education), ref = "Some college or university, no certificate or degree")
fit_multi_edu <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(Mushrooms_User ~ Education, data=drug_clean_2, family="binomial")
result3<-tidy(fit_multi_edu, conf.int=TRUE, exponentiate=TRUE)
print(result3)
```

---

## Mushroom User by Age

```{r, echo = FALSE}
ggplot(drug_clean_2, aes(x = Age, 
        fill = Mushrooms_User)) +
  geom_bar(position = "fill") +
  labs(x="Age Group",
       y = "Proportion",
       title="Figure 9: Mushroom User by Age",
       fill = "Mushrooms User") + 
  scale_fill_manual(values=c("#8a02b2","#560219")) 
```

---


## Logistic Regression: Age

```{r logistic-reg-age, echo = FALSE}
drug_clean_2$Age=relevel(factor(drug_clean_2$Age), ref = "18-24")
fit_multi_age <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(Mushrooms_User ~ Age, data=drug_clean_2, family="binomial")
result2<-tidy(fit_multi_age, conf.int=TRUE, exponentiate=TRUE)
print(result2)
```

---


## Density Plots: average personality scores of mushroom users and non-users

```{r trait-density-grid, echo = FALSE, , fig.height = 7, fig.width = 9}
Nscore.den <- ggplot(drug_clean, aes(Nscore))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6, show.legend=F) + 
  labs(title="Nscore", 
       subtitle="Neuroticism",
       x="Nscore") +
  scale_fill_manual(values=c("#8a02b2","#560219")) 

Escore.den <- ggplot(drug_clean, aes(Escore))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6, show.legend=F) + 
  labs(title="Escore", 
       subtitle="Extraversion",
       x="Escore") +
  scale_fill_manual(values=c("#8a02b2","#560219"))

Oscore.den <- ggplot(drug_clean, aes(Oscore))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6, show.legend=F) + 
  labs(title="Oscore", 
       subtitle="Openness to experience",
       x="Oscore") +
  scale_fill_manual(values=c("#8a02b2","#560219"))

Ascore.den <- ggplot(drug_clean, aes(AScore))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6, show.legend=F) + 
  labs(title="Ascore", 
       subtitle="Agreeableness",
       x="Ascore") +
  scale_fill_manual(values=c("#8a02b2","#560219"))

Cscore.den <- ggplot(drug_clean, aes(Cscore))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6, show.legend=F) + 
  labs(title="Cscore", 
       subtitle="Conscientiousness",
       x="Ascore") +
  scale_fill_manual(values=c("#8a02b2","#560219"))

Impulsive.den <- ggplot(drug_clean, aes(Impulsive))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6, show.legend=F) + 
  labs(title="Impulsive", 
       subtitle="Impulsiveness",
       x="Impulsive") +
  scale_fill_manual(values=c("#8a02b2","#560219"))

SS.den <- ggplot(drug_clean, aes(SS))+
  geom_density(aes(fill=factor(Mushrooms_User)), alpha=0.6) + 
  labs(title="SS", 
       subtitle="Sensation Seeking",
       x="SS",
       fill="Mushrooms Use") +
  theme(legend.position = c(3, 0.2)) +
  scale_fill_manual(values=c("#8a02b2","#560219"))

gridExtra::grid.arrange(Nscore.den, Escore.den, Oscore.den, Ascore.den, Cscore.den, Impulsive.den, SS.den, nrow = 3, top = "Figure 12: Average Personality Scores in Mushroom Users and Non-Users")
```

---

## Odds Ratio Estimates for Personality Traits

```{r logistic-personalities, echo = FALSE}
fit_multi_personality <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(Mushrooms_User ~ Nscore + Oscore + Impulsive + SS + Cscore + AScore + Escore, data=drug_clean_2, family="binomial")
result5<-tidy(fit_multi_personality, conf.int=TRUE, exponentiate=TRUE)
print(result5)
```

---


## Conclusions

--

- male gender, age category 18-24 years, an education status of “attended some college or university but have no certificate or degree” are all the most statistically significant indicators of mushroom use

--

- openness to experience is the personality trait that has the greatest statistically significant correlation to mushroom use

---

